

```{r}

library("tidyverse")
library("car")
library("SSBtools")
library("ggplot2")
library('moments')
library('corrr')
library('dplyr')
credit_data <- read.csv('/Users/Owner/Downloads/archive (1)/clean_dataset.csv',header= TRUE)
any(is.na(credit_data))
summary(credit_data)
```
Overview of the dataset. Then moodifying the categorial variables, eliminated Industry & Zipcode, transform continuous variables
```{r} 
New_credit_data <- credit_data %>%
  select(Gender,Age,Debt,Married,BankCustomer,Ethnicity,YearsEmployed,PriorDefault,Employed,CreditScore,DriversLicense,Income,Approved,Citizen) %>%
  mutate(Citizen_by_birth=ifelse(Citizen=='ByBirth',1,0)) %>%
  mutate(Citizen_by_others=ifelse(Citizen=='ByOtherMeans',1,0)) %>%
  mutate(Citizen_temp=ifelse(Citizen=='Temporary',1,0))%>%
  mutate(W= ifelse(Ethnicity=='White',1,0)) %>%
  mutate(B=ifelse(Ethnicity=='Black',1,0)) %>%
  mutate(A=ifelse(Ethnicity=='Asian',1,0)) %>%
  mutate(L=ifelse(Ethnicity=='Latino',1,0)) %>%
  mutate(O=ifelse(Ethnicity=='Other',1,0)) %>%
  mutate(log_age=log(Age))%>%
  mutate(log_debt=log(Debt+1)) %>%
  mutate(log_yearsemployed=log(YearsEmployed+1)) %>%
  mutate(log_income=log(Income+1))
  head(New_credit_data)
```
Final dataset to train, drop Ethnicity , citizen. Scale the dataset. 
```{r}
New_credit_data <-subset(New_credit_data,select=-c(Ethnicity,Citizen))
New_credit_data$Income <-scale(New_credit_data$Income)
```
Splitting data into training and testing 
```{r}
set.seed(1)
sample <- sample(c(TRUE,FALSE),nrow(New_credit_data),replace=TRUE,prob=c(0.7,0.3))
train <- New_credit_data[sample,]
test <-New_credit_data[!sample,]
```
PCA transform 
```{r}
PCA_data <- prcomp(train,scale=TRUE,center=TRUE)
summary(PCA_data)
var_explained= PCA_data$sdev^2/sum(PCA_data$sdev^2)
which(cumsum(var_explained) >=0.9)
```
Plotting elbow when it is finalized.The first 15 variables are able explaining 94% of the variances
Creating predict model using the first 14 factors
#reverse the signs & displaying principal componnents.
```{r}
PCA_data$rotation <- -1*PCA_data$rotation
PCA_data$rotation
```
EXTRACTING 15 pc FOR TRAIN AND TEST DATASET
```{r}
mydata <- data.frame(Class= train[,"Approved"],PCA_data$x[,1:15])
head(mydata)
```
Build logistic model 
```{r}
model <-glm(Class~.,data=mydata,family='binomial')
summary(model)
```
Predict on the test set data
```{r}
test.p <-predict(PCA_data,newdata=test)
pred <-predict(model,newdata=data.frame(test.p[,1:15]),type="response")
```
Displaying the cross classification table
```{r}
predApproved <-factor(ifelse(pred>=0.5,"0","1"))
table(test$Approved,predApproved)
```
  
  